### 2013-03-23 doc/sosp13/tasks.tex

Tasks are not allocated any execution resources until the scheduler
decides to run them; when this occurs, tasks are matched with {\em
  worker} threads. Each worker is simply a collection of status bits and a
stack, allocated at a particular core.

\paragraph{Context switching} Grappa context switches between tasks
non-preemptively. As with other cooperative multithreading systems, we
treat context switches as function calls, saving and restoring only the
callee-saved state as specified in the x86-64 ABI \cite{amd64:abi:2012}. This
involves saving six general-purpose 64-bit registers and the stack
pointer, as well as the 16-bit x87 floating point control word and the
SSE context/status register. Thus, the minimum amount of state a
cooperative context switch routine must save according to the ABI is 62
bytes.

>>>>

Tasks are not allocated any execution resources until the scheduler
decides to run them; when this occurs, tasks are matched with {\em
  worker\/} threads. Each worker is simply a collection of status bits and a
stack, allocated at a particular core.

\paragraph{Context switching} Grappa context switches between tasks
non-preemptively. As with other cooperative multithreading systems, we
treat context switches as function calls, saving and restoring only the
callee-saved state as specified in the x86-64 ABI \cite{amd64:abi:2012}. This
involves saving six general-purpose 64-bit registers and the stack
pointer, as well as the 16-bit x87 floating point control word and the
SSE context/status register. Thus, the minimum amount of state a
cooperative context switch routine must save, according to the ABI, is
62~bytes.
